Local PCA Shows How Population Structure Differs Along the Genome

### 2016-06-08 writeup/local_pca_paper.tex
update

\begin{figure}
    \begin{center}
       \includegraphics{Fig4_temp}
    \end{center}
    \caption{
         Variation in structure between windows on human chromosomes 8, 15, and 17. 
         Each point in the plot represents a window.
         The first column shows the MDS visualization of relationships between windows;
         the second and third columns show the two MDS coordinates of each window against its position (midpoint) along the chromosome. 
         Rows, from top to bottom show chromosomes 8, 15, and 17. 
         The vertical red lines show the breakpoints of the known inversions \citep{antonacci2009characterization}.
        \label{fig:mds_human}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics{Medicago_MDS_1D_and_gene_count}
    \end{center}
    \caption{
         MDS results and gene density for the \textit{Medicago} genome (chromosome 1-8). 
         For each chromosome, the red plot above is first coordinate of MDS against the middle position of each window along each chromosome. 
         The black plot below is gene count for each window against the position of each window.
         \label{fig:mds_medicago}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics{medicago_mds}
    \end{center}
    \caption{
     MDS visualization for Medicago chromosome 3. Each point in the plot stands for a window (length 1000 SNPs).
       \label{fig:mds12_medicago}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics{medicago_peaks_pca}
    \end{center}
    \caption{
        PCA plots for the three sets of genomic windows colored separately in Figure \ref{fig:mds12_medicago}. 
        From left to right, the windows colored green, orange, and purple. Each point corresponds to a sample, colored by origin.
        \label{fig:pca_medicago}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{Fig4_POPRES_Together_MDS_plot_chr8_15_17}
    \end{center}
    \caption{
         Variation in structure between windows on human chromosomes 8, 15, and 17. 
         Each point in the plot represents a window.
         The first column shows the MDS visualization of relationships between windows;
         the second and third columns show the two MDS coordinates of each window against its position (midpoint) along the chromosome. 
         Rows, from top to bottom show chromosomes 8, 15, and 17. 
         The vertical red lines show the breakpoints of the known inversions \citep{antonacci2009characterization}.
        \label{fig:mds_human}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{Fig5_MDS_and_gene_count_allchr}
    \end{center}
    \caption{
         MDS results and gene density for the \textit{Medicago} genome (chromosome 1-8). 
         For each chromosome, the red plot above is first coordinate of MDS against the middle position of each window along each chromosome. 
         The black plot below is gene count for each window against the position of each window.
         \label{fig:mds_medicago}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{Fig6_Together_MDS_plot_chr3_final}
    \end{center}
    \caption{
     MDS visualization for Medicago chromosome 3. Each point in the plot stands for a window (length 1000 SNPs).
       \label{fig:mds12_medicago}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{Fig7_pca_plots_for_Medicago_chr3_3peaks_byMDS}
    \end{center}
    \caption{
        PCA plots for the three sets of genomic windows colored separately in Figure \ref{fig:mds12_medicago}. 
        From left to right, the windows colored green, orange, and purple. Each point corresponds to a sample, colored by origin.
        \label{fig:pca_medicago}
    }
\end{figure}
